---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# googlesheets.reader

<!-- badges: start -->
<!-- badges: end -->

A lightweight R package, `googlesheetsReader`, intended to make reading data from Google Sheets easier. It uses the googlesheets4 package to effortlessly retrieve and analyze data from any sheet in a Google Sheets document, providing a clean and convenient interfacefor R users. Streamline your workflow with this easy-to-use package for seamless integration with Google Sheets data in your R projects.

## Installation

You can install the development version of googlesheets.reader from [GitHub](https://github.com/) with:

```{r}
# install.packages("devtools")
devtools::install_github("danymukesha/googlesheets.reader")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(googlesheets.reader)
google_sheets_url <- "https://docs.google.com/spreadsheets/d/1U6Cf_qEOhiR9AZqTqS3mbMF3zt2db48ZP5v3rkrAEJY/edit#gid=780868077"
result <- read_google_sheets(google_sheets_url)
```

Replace "google_sheets_url" with the actual URL for your google sheet.

```{r}
head(result)
```

